Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-02-20 products/manuscript/Manuscript.qmd
Introduction

@@

@@

@@

https://pubmed.ncbi.nlm.nih.gov/32981858/
https://pubmed.ncbi.nlm.nih.gov/30687521/ #This study is set in Senegal 
https://www.sciencedirect.com/science/article/pii/S001078241730478X

>>>>

We will be looking for patterns in contraceptive methods and higher unintended pregnancies across age groups (20-24) and (35-49) to investigate the effectiveness of each contraceptive method.Financial, social, religious, and cultural factors are current challenges against efforts towards reducing unintended pregnancies. According to a cross-sectional survey done in 2017, contraceptive use was prevalent among women who had attained higher education, were in stable partnerships, and identified with the dominant ethnic group. Additionally, factors like previous pregnancies and immigration status did not appear to influence contraceptive use in this study. The table provided above under `Summarize the data` shows that African and Latin American/Caribbean countries have the highest percentages of unintended pregnancies. This could be due to the current legal status of contraception within Latin American countries. Free emergency contraception access exists, but regulations differ. Chile, Colombia, and Ecuador legally recognize access, while Nicaragua and Bolivia rely on Ministerial protocols. Argentina and Brazil lack legal recognition, but offer protocols and guides. Mexico requires provision to victims of sexual and domestic violence (Hevia, 2012).

@@

This data originates from the Guttmacher Institute's Adding It Up project. The data contains numeric variables: percentages of pregnancy outcomes, rates of safe and unsafe abortions, percentage of various contraceptive usages, percentages of care received for various pregnancy complications, and costs for many variables including abortions and STIs. There are only three  character variables that can be used to group the numeric variables: country name, region, and sub region. So far we have dvided the observations into "low", "medium", and "high" category of birth control usage.

@@

1. How does marriage status affect percentage of unintended pregnancies across different types of birth control?

2. Is there a significant difference in the percentage of unplanned pregnancies between reversible contraceptives (LARCs?) among the age groups (20-24) and (35-49)?

@@

https://pubmed.ncbi.nlm.nih.gov/32981858/
https://pubmed.ncbi.nlm.nih.gov/30687521/ #This study is set in Senegal 
https://www.sciencedirect.com/science/article/pii/S001078241730478X 
https://www.sciencedirect.com/science/article/abs/pii/S0020729211005406 #legal status article
